Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-01-11 src/tex/ms.tex
[showyourwork] overleaf sync

With the publication of larger and more detailed datasets \cite{ludwig_dataset_2022}, the risk estimation models may be extended as well to include the additionally reported \glspl{lnl} V and VII. This work aims to do that and at the same time demonstrate the capability 
of the previously introduced \gls{hmm} to adapt to real patient data from a multi-centric cohort of XXX \gls{opscc} patients.

>>>>

With the publication of larger and more detailed datasets \cite{ludwig_dataset_2022}, the risk estimation models may be extended as well to include the additionally reported \glspl{lnl} V and VII. This work aims to do that and at the same time demonstrate the capability 
of the previously introduced \gls{hmm} to adapt to real patient data from a multi-centric cohort of \variable{output/num_patients.txt} \gls{opscc} patients.
